Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-10-30 paper/pool_model.tex
remove unused footnotes
flatten file structure of images

\tnotetext[t1]{TODO}
\tnotetext[t2]{TODO}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/TPM_fig.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource.pdf}

@@

    %\includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_3pools_resource_tempshift2.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2pools_resource_competition.pdf}

@@

    %\includegraphics[width=\columnwidth]{Figures/pool_model_2pools_toxin.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2pools_toxin1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2pools_toxin2.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib2.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_1pool_inhib3.pdf}

@@

    %\includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop1.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop2.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures/pool_model_2sp_1pool_coop3.pdf}

@@

%     \includegraphics[width=0.6\textwidth]{Figures/interaciton_potential.png}

@@

        {Figures/snapshot-2-cells-before-division.png}%

@@

        {Figures/snapshot-2-cells-after-division.png}

@@

        {Figures/abm-homogenous/images/snapshot_00006000.png}

@@

        {Figures/abm-homogenous/images/snapshot_00012000.png}

@@

        {Figures/abm-homogenous/images/snapshot_00018000.png}

@@

        {Figures/abm-homogenous/images/snapshot_00024000.png}

@@

        \includegraphics[width=\columnwidth]{Figures/abm-homogenous/abm_ode_comparison.png}

@@

        \includegraphics[width=\columnwidth]{Figures/abm-homogenous-low-diffusion/abm_ode_comparison.png}

@@

        \includegraphics[width=\columnwidth]{Figures/abm-inhomogenous/abm_ode_comparison.png}%

@@

        \includegraphics[width=\columnwidth]{Figures/abm-random/abm_ode_comparison.png}%

@@

        \includegraphics[width=\textwidth]{Figures/abm-homogenous/images/snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-homogenous-low-diffusion/images/snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous/images/snapshot_00012000.png}%

@@

        \includegraphics[width=\textwidth]{Figures/abm-random/images/snapshot_00012000.png}%

>>>>

@@

    \includegraphics[width=0.9\columnwidth]{Figures-TPM_fig.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_3pools_resource.pdf}

@@

    %\includegraphics[width=0.9\columnwidth]{Figures-pool_model_3pools_resource_tempshift.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_3pools_resource_tempshift1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_3pools_resource_tempshift2.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_2pools_resource_competition.pdf}

@@

    %\includegraphics[width=\columnwidth]{Figures-pool_model_2pools_toxin.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_2pools_toxin1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_2pools_toxin2.pdf}

@@

    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_1pool_inhib1.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_1pool_inhib2.pdf}\\
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_1pool_inhib3.pdf}

@@

    %\includegraphics[width=0.9\columnwidth]{Figures-pool_model_2sp_1pool_coop.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_2sp_1pool_coop1.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_2sp_1pool_coop2.pdf}
    \includegraphics[width=0.9\columnwidth]{Figures-pool_model_2sp_1pool_coop3.pdf}

@@

%     \includegraphics[width=0.6\textwidth]{Figures-interaciton_potential.png}

@@

        {Figures-snapshot-2-cells-before-division.png}%

@@

        {Figures-snapshot-2-cells-after-division.png}

@@

        {Figures-abm-homogenous-images-snapshot_00006000.png}

@@

        {Figures-abm-homogenous-images-snapshot_00012000.png}

@@

        {Figures-abm-homogenous-images-snapshot_00018000.png}

@@

        {Figures-abm-homogenous-images-snapshot_00024000.png}

@@

        \includegraphics[width=\columnwidth]{Figures-abm-homogenous-abm_ode_comparison.png}

@@

        \includegraphics[width=\columnwidth]{Figures-abm-homogenous-low-diffusion-abm_ode_comparison.png}

@@

        \includegraphics[width=\columnwidth]{Figures-abm-inhomogenous-abm_ode_comparison.png}%

@@

        \includegraphics[width=\columnwidth]{Figures-abm-random-abm_ode_comparison.png}%

@@

        \includegraphics[width=\textwidth]{Figures-abm-homogenous-images-snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures-abm-homogenous-low-diffusion-images-snapshot_00012000.png}

@@

        \includegraphics[width=\textwidth]{Figures-abm-inhomogenous-images-snapshot_00012000.png}%

@@

        \includegraphics[width=\textwidth]{Figures-abm-random-images-snapshot_00012000.png}%
